%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Invited Talks}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    \cventryshort
    {Seminar at Samsung Advanced Institute of Technology}
    {Guiding Deep Molecular Optimization with Genetic Exploration}
    {Dec. 2020}
    {Suwon, Republic of Korea}
    \vspace{.1in}

%---------------------------------------------------------
  \cventryshort
    {AI \& CSE Seminar at Pohang University of Science and Technology (POSTECH)}
    {Scaling Deep Reinforcement Learning to Large Combinatorial Problems}
    {Feb. 2020}
    {Pohang, Republic of Korea}
    \vspace{.1in}

%---------------------------------------------------------
  \cventryshort
    {Robotics Seminar at University of Oxford}
    {Bucket-Renormalization for Approximate Inference}
    {Jul. 2018}
    {Oxford, England}
    \vspace{.1in}
    
%---------------------------------------------------------
  \cventryshort
    {Physics Informed Machine Learning Workshop}
    {Mini Bucket-Renormalization}
    {Feb. 2018}
    {Santa Fe, New Mexico, U.S}
    \vspace{.1in}
    
%---------------------------------------------------------
  \cventryshort
    {CNLS Student Seminar at Los Alamos National Laboratory (LANL)}
    {Gauge Transformation of Graphical Models}
    {Jul. 2017}
    {Los Alamos, New Mexico, U.S}
    \vspace{.1in}

%---------------------------------------------------------
  \cventryshort
    {Banff Workshop on Optimization and Inference for Physical Flows on Networks}
    {Optimizing Gauge Transformation for Inference in Graphical Model}
    {Feb. 2017}
    {Banff, Alberta, Canada}
    \vspace{.1in}

%---------------------------------------------------------
  \cventryshort
    {CNLS Student Seminar at Los Alamos National Laboratory (LANL)}
    {Synthesis of MCMC and Belief Propagation}
    {Jul. 2016}
    {Los Alamos, New Mexico, U.S}
    \vspace{.1in}

%---------------------------------------------------------
  \cventryshort
    {Discrete Math Seminar at Korea Advanced Institute of Science and Technology (KAIST)}
    {Minimum Weight Perfect Matching via Blossom Belief Propagation}
    {Nov. 2015}
    {Daejeon, Republic of Korea}
    \vspace{.1in}
    
\end{cventries}
