\documentclass[11pt]{article}

% # FONTS

\usepackage[T1]{fontenc}
\renewcommand*\ttdefault{lmvtt}
%\usepackage[bitstream-charter]{mathdesign}
\usepackage{amsmath}
%\usepackage[scaled=0.92]{PTSans}
%\usepackage{charter}
% # GEOMETRY

\usepackage[
  paper  = letterpaper,
  left   = 1.0in,
  right  = 1.0in,
  top    = 1.25in,
  bottom = 1.25in,
]{geometry}
%\usepackage[final,expansion=alltext]{microtype}
\usepackage[english]{babel}
\usepackage[parfill]{parskip}
\usepackage{afterpage}
\usepackage{framed}
\usepackage{enumitem}
\usepackage{pifont}     % needed for dingbats for colophon

% # COLOR
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{shadecolor}{gray}{0.9}
\definecolor{WineRed}{rgb}{0.6,0,0}

\usepackage[colorlinks=true,urlcolor=WineRed,citecolor=WineRed]{hyperref}

% # MACROS

\newcommand{\me}[1]{\textbf{#1}}
% Add this to compile in Overleaf.
% \usepackage{natbib}

% # HEADERS

\usepackage{fancyhdr}
\fancyhf{}
\pagestyle{fancy}
\lhead{\textcolor{gray}{\emph{Sungsoo Ahn}}}
\rhead{\textcolor{gray}{\thepage}}
\renewcommand{\headrulewidth}{0pt}

% Renew section
\renewcommand{\section}[1]
{\vspace{1.0\baselineskip}{\Large\textbf{#1}}}

\begin{document}
\thispagestyle{empty}


\begin{center}
    {\Huge \bf Sungsoo Ahn} \vspace{.2in} \\
    %{\Large Sungsoo Ahn}\\
    Korea Advanced Institute of Science and Technology (KAIST)\\
    {E-mail:} \texttt{sungsoo.ahn@kaist.ac.kr}, {Mobile:} \texttt{(+82)10-9495-1392}, \\
    {Web:} \href{https://sungsoo-ahn.github.io}{\texttt{sungsoo-ahn.github.io}}
\end{center}
%\parbox[c][0.5in]{3.4in}{{\huge \textbf{Sungsoo Ahn}}}\\
%{\small 
%}
\section{Education}
\begin{itemize}
    \item[] MS/Ph.D Integrated Course in Electrical Engineering \hfill Mar. 2015 -- Mar. 2021\\
    \textit{Korea Advanced Institute of Science and Technology (KAIST),
    Daejeon, South Korea} \\
    \textit{Advisor: Jinwoo Shin}
    \item[] BS in Electrical Engineering \hfill Mar. 2011 -- Mar. 2015\\
    \textit{Korea Advanced Institute of Science and Technology (KAIST), 
    Daejeon, South Korea}
\end{itemize}
\section{Employment}
\begin{itemize}
\item[] Assistant Professor \hfill Jan. 2025 -- Present \\
\textit{Korea Advanced Institute of Science and Technology (KAIST), Daejeon, South Korea}
\item[] Assistant Professor \hfill Dec. 2021 -- Jan. 2025 \\
\textit{Pohang University of Science and Technology (POSTECH), Pohang, South Korea}\\
\textit{Graduate School of AI and Department of Computer Science and Engineering}
\item[] Research Associate \hfill Mar. 2021 -- Nov. 2021 \\
\textit{Mohamed Bin Zayed University of Artificial Intelligence (MBZUAI), \\
Abu Dhabi, United Arab Emirates} \\
\textit{Supervisors: Le Song and Eric Xing}
\item[] Research Intern \hfill Jun. 2018 -- Aug. 2018 \\
\textit{Amazon Cambridge Development Center, Cambridge, England} \\
\textit{Supervisor: Zhenwen Dai}
\item[] Visiting Student \hfill Mar. 2018 -- May 2018 \\
\textit{University of Cambridge, Cambridge, England} \\
\textit{Host: Adrian Weller}
\item[] Research Intern \hfill Jun. 2017 -- Aug. 2017\\
\textit{Los Alamos National Laboratory, New Mexico, United States}\\
\textit{Host: Michael Chertkov}
\item[] Research Intern \hfill Jun. 2016 -- Aug. 2016\\
\textit{Los Alamos National Laboratory, New Mexico, United States}\\
\textit{Host: Michael Chertkov}
\end{itemize}

\newpage
\section{Publications}
{\small $^*$Equal contribution. $^\dagger$Corresponding author.}\par
\input{publications}

\section{Services}

\begin{enumerate}
  \item Local Chair, Probabilistic Machine Learning Conference (ProbML) \hfill 2026
  \item Workshop Organizer, International Conference on Machine Learning (ICML), AI4Science \hfill 2026
  \item Area Chair, International Conference on Machine Learning (ICML) \hfill 2022 -- 2026
  \item Area Chair, International Conference on Learning Representations (ICLR) \hfill 2024 -- 2026
  \item Area Chair, Conference on Neural Information Processing Systems (NeurIPS) \hfill 2022 -- 2025
  \item Area Chair, Intl. Conference on Artificial Intelligence and Statistics (AISTATS) \hfill 2022 -- 2024
  \item Area Chair, Association for the Advancement of Artificial Intelligence (AAAI) \hfill 2024
  \item Action Editor, Transactions of Machine Learning Research (TMLR) \hfill 2024 -- 2026
  \item Workflow Chair, International Conference on Machine Learning (ICML) \hfill 2022
  \item Board of Directors, Korean Society of AI Frontier (KSAIF) \hfill 2025 --
  \item Reviewer, NeurIPS \hfill 2018 -- 2021
  \item Reviewer, ICML \hfill 2019 -- 2021
  \item Reviewer, ICLR \hfill 2019 -- 2024
  \item Reviewer, AISTATS \hfill 2019 -- 2021
\end{enumerate}

\section{Talks}

\begin{enumerate}
\item Foundation Models for Material Discovery \hfill Jul. 2025\\
\textit{Korea Institute of Material Science (KIMS), Changwon, South Korea}
\item Generative Models for Molecular Discovery \hfill Jul. 2025\\
\textit{Seoul National University, Seoul, South Korea}
\item A Generative Model for Metal Organic Frameworks \hfill Jul. 2025\\
\textit{KAIST-MILA Annual Workshop, Montreal, Canada}
\item Machine Learning for Transition Path Sampling \hfill Jul. 2025\\
\textit{Korean In silico bio Design and Discovery Society (KIDDS), Daejeon, South Korea}
\item Generative Models for Molecular Discovery \hfill May. 2025\\
\textit{LG AI Research, Seoul, South Korea}
\item Optimization Methods for Material Science \hfill Dec. 2024\\
\textit{POSCO Holdings, Seoul, South Korea}
\item Structure- and Energy-Based Machine Learning for Molecules \hfill Dec. 2024\\
\textit{KAIST-MILA Prefrontal AI Workshop, Montreal, Canada}
\item Amortizing Intractable Inference for Molecular Discovery \hfill Nov. 2024\\
\textit{Physics Informed Machine Learning Workshop, New Mexico, United States}
\item Opportunities and Challenges in Deep Graph Generative Models \hfill Nov. 2023\\
\textit{AI Korea, Seoul, South Korea}
\item Machine Learning for Drug Discovery \hfill Oct. 2023\\
\textit{Korea Advanced Institute of Science and Technology (KAIST), Daejeon, South Korea}
\item Graph Structured Prediction and Graph Generation with Deep Learning \hfill Jun. 2023\\
\textit{Korea Advanced Institute of Science and Technology (KAIST), Daejeon, South Korea}
\item Deep Neural Networks for Graph Optimization \hfill Nov. 2022\\
\textit{University of Arizona, Arizona, United States}
\item Geometric Deep Learning for Drug Discovery \hfill Aug. 2022\\
\textit{Korean Artificial Intelligence Association (KAIA), Jeju, South Korea}
\item Machine Learning for Drug Discovery \hfill Jun. 2022\\
\textit{Centre for Frontier AI Research, Singapore}
\item Elimination Techniques in Probabilistic Graphical Models \hfill Jun. 2021\\
\textit{Skolkovo Institute of Science and Technology (Skoltech), Moscow, Russia}
\item Guiding Deep Molecular Optimization with Genetic Exploration \hfill Dec. 2020\\
\textit{Samsung Advanced Institute of Technology (SAIT), Suwon, South Korea}
\item Scaling Deep Reinforcement Learning to Large Combinatorial Problems \hfill Feb. 2020\\
\textit{Pohang University of Science and Technology (POSTECH), Pohang, South Korea}
\item Bucket Renormalization for Approximate Inference \hfill Jul. 2018\\
\textit{University of Oxford, Oxford, England}
\item Mini-Bucket Renormalization \hfill Feb. 2018\\
\textit{Physics Informed Machine Learning Workshop, Santa Fe, New Mexico, United States}
\item Gauge Transformation of Graphical Models \hfill Jul. 2017\\
\textit{Los Alamos National Laboratory (LANL), New Mexico, United States}
\item Optimizing Gauge Transformation for Inference in Graphical Models \hfill Feb. 2017\\
\textit{Banff Workshop, Alberta, Canada}
\item Synthesis of MCMC and Belief Propagation \hfill Jul. 2016\\
\textit{Los Alamos National Laboratory (LANL), New Mexico, United States}
\item Minimum Weight Perfect Matching via Blossom Belief Propagation \hfill Nov. 2015\\
\textit{Korea Advanced Institute of Science and Technology (KAIST), Daejeon, South Korea}
\end{enumerate}

\section{Courses}
\begin{enumerate}
\item Proteins and AI (CoE499) \hfill Spring 2026\\
\textit{Korea Advanced Institute of Science and Technology (KAIST)}
\item Machine learning for molecules (AI899) \hfill Fall 2025\\
\textit{Korea Advanced Institute of Science and Technology (KAIST)}
\item Geometric deep learning (AI810) \hfill Spring 2025\\
\textit{Korea Advanced Institute of Science and Technology (KAIST)}
\item Introduction to artificial intelligence (CSED105) \hfill Fall 2024\\
\textit{Pohang University of Science and Technology (POSTECH)}
\item Machine learning for graphs (CSED/AIGS703I) \hfill Spring 2024\\
\textit{Pohang University of Science and Technology (POSTECH)}
\item Introduction to artificial intelligence (CSED105) \hfill Fall 2023\\
\textit{Pohang University of Science and Technology (POSTECH)}
\item Probabilistic graphical models (CSED/AIGS524) \hfill Spring 2023\\
\textit{Pohang University of Science and Technology (POSTECH)}
\item Introduction to machine learning (CSED490B) \hfill Fall 2022\\
\textit{Pohang University of Science and Technology (POSTECH)}
\item Probabilistic graphical models (CSED/AIGS524) \hfill Spring 2022\\
\textit{Pohang University of Science and Technology (POSTECH)}
\end{enumerate}
\section{Awards}
\begin{enumerate}
\item NVIDIA Academic Grant Program Award \hfill Spring 2025
\item KAIST Q-Day Award \hfill Winter 2025
\item KAIST Outstanding Teaching Award \hfill Spring 2026
\end{enumerate}
\end{document}
